Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
add preta mixing discussion

\twocolumn[
\maketitle
\begin{onecolabstract}
  \begin{quote}\begin{quote}\begin{quote}
  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems that replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both \term{verifiable} and \term{secret}
	and analyze how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
	use cryptographic techniques to meet those goals.
	\end{quote}\end{quote}\end{quote}
  \vspace{1em}
\end{onecolabstract}
]

@@

For example, at an in-person polling location -- ignoring ballot secrecy (see below) -- a voter
could be shown a screen giving the name of the candidate(s) she just voted for. If the display
does not match the voter's intention, then the voter can try again -- or call into question the
entire vote collection process.

@@

Even in a receipt-free system,
if the voting process involves a multi-step interaction involving the coercer,
it may be possible for the voter to prove to the coercer that she is following
some protocol \cite{delaune}.
A simple example that is common to many proposed voting systems is
the \term{Italian attack} \cite{preta}.
This problem arises when the ballot contains a large number of voting options,
such as a ranked election in which the number of possibilities grows as the
factorial of the number of candidates.
If the voter and coercer have one interaction prior to voting,
they can follow this protocol:
\begin{enumerate}
\item A coercer who favors candidate $c_1$ randomly permutes $[2, n]$ and
communicates the resulting permutation $\pi$ to the voter.
\item The voter casts a ballot ranking candidates in the order
$c_1, c_{\pi(2)}, c_{\pi(3)}, \ldots$.
\item The coercer, seeing the resulting ballot in the published list of votes,
is assured that it was cast by the voter with probability
$\ge 1 - \frac{v}{(n-1)!}$, where $v$ is the number of voters.
\end{enumerate}

@@

Table S contains final vote tallies. Each column represents a particular candidate, and there will
be one marked cell in each column for each ballot cast for that candidate.

@@

All candidates are listed on the optical-scan ballot, and the voter makes her choice by filling
in a bubble that reveals an alphanumeric confirmation code (as specified in the private Table
P), which the voter then records on the receipt portion. The ballot is sent through an optical
scanner, and the voter takes her receipt when leaving the polling location. It can later be
compared against published Table Q to ensure that the vote was recorded properly.

Additionally, during the voting process, a voter can ask a poll worker for an second \term{audit}
ballot. This ballot is initially just like any other ballot: however, \emph{all} candidate codes are
revealed, and the ballot is marked as an audit ballot. An audit ballot is scanned, but the voter is
allowed to keep the ballot for later verification. This verification process is described and
discussed in our analysis.

@@

When a ballot has been received, the following takes place:
\begin{enumerate}
	\item
		The candidate code is revealed in Table Q. (If this is an audit ballot -- see below -- then all
		are revealed, and we'll perform the following steps for each code.)
	\item
		A check mark is placed on the row in Table R that maps the revealed Q value to some value in S.
	\item
		The Table R mapping is followed into Table S, and a check mark is added to a cell in Table R,
		to be counted as a vote for that row's candidate.
\end{enumerate}

@@

Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous, even to the officials performing the encryption, by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.

@@

When a voter goes to cast a vote, her candidate selection is encrypted locally (i.e., on her
computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
presented with a SHA-1 hash of her encrypted ballot. At this point, the voter may choose either
to submit the ballot or to audit it. In the former case, the ballot is cast and voting is
complete. But when a voter chooses to audit, she is presented with \emph{all} of the data
used to encrypt the vote. Namely, this includes the public key and the randomness that were used
by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
which allows randomness to be specified -- perform the encryption and SHA-1 hash herself
to verify that the hash that \emph{would} have been cast actually does represent the ballot she
intended to cast.

@@

Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
\term{mixnet}.

@@

The mixnet accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
same key, but with different random inputs). A random permutation -- referred to as $\pi_{N}$ (where
$N$ is the total number of votes) -- is first used to perform the shuffle. Each ciphertext
$c_{i}$ is then \term{re-encrypted} to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
the random input at encrypt time been different} by a particular amount $s_{i}$. See Figure
~\ref{fig:mixnet} for a visual depiction of this process.

The \term{shuffling} is important because it prevents an attacker from linking a decrypted ballot with
a particular encrypted ballot -- and thus a voter. Re-encryption means that an auditor examining a
proof of proper decryption cannot determine how a particular voter cast her ballot by hashing
all ciphertexts in the proof and matching those hashes to the publicly-posted encrypted vote hashes.

In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
times, actually using only the final shuffle in tallying the results. The other shuffles,
referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
other bit value indicating that it must provide a mapping from one shadow mix to another. This is
known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
obtain the set of challenges allows this process to be completed entirely within the Helios system
-- without human involvement -- for publication and auditor verification.

@@

Each of these systems provides ballot secrecy by performing a three-step process:
\begin{enumerate}
	\item
		Encrypt ballot prior to its being cast.
	\item
		Mix the ballots in some way.
	\item
		Reveal decrypted ballots for tallying.
\end{enumerate}

@@

In Scantegrity, public version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, keyless encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.)

In Helios, the public ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
which -- unlike Scantegrity's core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, Helios uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about Helios's
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees. Scantegrity essentially has an immensely large
key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
decrypted. Helios, however, uses known algorithms with shorter keys that could potentially be
attacked. Compromise of keys in either system would destroy their privacy guarantees.

@@

Essentially, both Scantegrity and Helios use some mechanism to shuffle votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

In Scantegrity, the ballot mix is predetermined, as it is defined by the generation of Table R.
When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
ballots, the information revealed that is ultimately revealed allows half of the ballots to be
traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
Should Table P be compromised, one could complete all mappings and violate secrecy entirely -- or
simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
\emph{either} size of Table R to votes in Table Q \emph{or} tallies in Table S be deterministic,
privacy would be compromised for half of all voters.

Where Table R lies between encryptions and decryptions in Scantegrity, Helios makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in Scantegrity, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

@@

At the time a ballot is cast, both Scantegrity and Helios attempt to ensure a voter that her
vote is recorded exactly as intended.

@@

Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

@@

A common theme in verifiable voting systems seems to be the presence of a published \term{bulletin
board} of votes. Note that because these boards contain only encrypted information, they do not
violate ballot secrecy.

@@

Secondly, recall that for each row in Table R that does not represent an audit ballot, only half of
the Q-to-S mapping is revealed; \emph{which} half is uncovered is chosen randomly. This prevents an
auditor from mapping any cast ballot to its chosen candidate, but it permits \emph{partial}
verification by allowing an observer to note that the following are true:
\begin{itemize}
	\item
		If a row in Table R is \textbf{checked} and its mapping to Table Q is revealed, then the
		corresponding cell in Table Q has a \textbf{revealed} confirmation code (indicating that the
		code was revealed on a ballot).
	\item
		If a row in Table R is \textbf{unchecked} and its mapping to Table Q is revealed, then the
		corresponding cell in Table Q has a \textbf{hidden} confirmation code (indicating that the code
		was \emph{not} revealed on a ballot).
	\item
		If a row in Table R is \textbf{checked} and its mapping to Table S is revealed, then the
		corresponding cell in Table S is \textbf{checked} (indicating an addition to a candidate's
		tally).
	\item
		If a row in Table R is \textbf{unchecked} and its mapping to Table S is revealed, then the
		corresponding cell in Table S is \textbf{unchecked} (indicating \emph{no} addition to a
		candidate's tally).
\end{itemize}
This technique -- verifying a random partial sample of the data -- is called \term{randomized partial
checking}. If these checks past, it is accepted that all other ballots must also be counted properly.

@@

Scantegrity prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
without exposure of the data maintained in Table P -- Scantegrity's secret -- the voter has no
way to prove to a third party that the claim is true.

An important point regarding Scantegrity is that it also relies on a \emph{physical property} -- the
invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
the person for having voted a certain way). This is akin to keeping Table P a secret: the ballots
together \emph{are} Table P, and using special ink allows the codes to be printed without making it
easy for a ballot handler to simple read Table P from the ballots prior to the election.

Helios, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
physical security aside: as with Scantegrity, Helios does not reveal to a voter all the
information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus convincing the coercer
of something untrue.
This is one reason that it is important for the system to use a collision-resistant hash function.

@@

The public nature of this information can combat ballot stuffing. If names are associated with
the posted ballots, then it should be obvious to one or more careful observers (given sufficient
resources) that nonexistent persons are being posted. Furthermore, publication of ballots
per-precinct can reveal stuffing should the number of ballots being reported by a particular
precinct/polling location be significantly higher than expected \cite{helios}.

@@

One might wish to prevent a party from determining who did or did not cast \emph{any} ballot.
As we've seen, \term{verifiable counting} typically relies on the public nature of this data.
Additionally, should this data be hidden, it could potentially be more difficult to notice ballot
stuffing.

@@

In each of these key systems, there exists some way to tie a vote back to a voter or to a physical
receipt: there is always some secret. Ideally, there would be a system wherein a vote could be
tallied properly without \emph{anyone} being able to reveal the candidate selected on the ballot.
Admittedly, to achieve this would be difficult: in the case of a single vote, tallying only that vote
would reveal the candidate for which it was cast. But if a secret \emph{must} be kept, it is
worthwhile to take precautions to minimize risk of compromise.

>>>>

\twocolumn[
\maketitle
\begin{onecolabstract}
  \begin{quote}\begin{quote}\begin{quote}
  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems that replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
	how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
	use cryptographic techniques to meet those goals.
	\end{quote}\end{quote}\end{quote}
  \vspace{1em}
\end{onecolabstract}
]

@@

For example, at an in-person polling location -- ignoring ballot secrecy (see below) -- a voter
could be shown a screen giving the name of the candidate(s) she just voted for. If the display
does not match the voter's intention, then the voter can ``try again'' -- or call into question the
entire vote collection process.

@@

Even in a receipt-free system,
if the voting process involves a multi-step iteraction involving the coercer,
it may be possible for the voter to prove to the coercer that she is following
some protocol \cite{delaune}.
A simple example that is common to many proposed voting systems is
the \term{Italian attack} \cite{preta}.
This problem arises when the ballot contains a large number of voting options,
such as a ranked election in which the number of possibilities grows as the
factorial of the number of candidates.
If the voter and coercer have one interaction prior to voting,
they can follow this protocol:
\begin{enumerate}
\item A coercer who favors candidate $c_1$ randomly permutes $[2, n]$ and
communicates the resulting permutation $\pi$ to the voter.
\item The voter casts a ballot ranking candidates in the order
$c_1, c_{\pi(2)}, c_{\pi(3)}, \ldots$.
\item The coercer, seeing the resulting ballot in the published list of votes,
is assured that it was cast by the voter with probability
$\ge 1 - \frac{v}{(n-1)!}$, where $v$ is the number of voters.
\end{enumerate}

@@

Table S contains final vote tallies. Each column represents a particular candidate, and there will
be one ``checked'' cell in each column for each ballot cast for that candidate.

@@

All candidates are listed on the optical-scan ballot, and the voter makes her choice by filling
in a ``bubble'' that reveals an alphanumeric confirmation code (as specified in the private Table
P), which the voter then records on the receipt portion. The ballot is sent through an optical
scanner, and the voter takes her receipt when leaving the polling location. It can later be
compared against published Table Q to ensure that the vote was recorded properly.

Additionally, during the voting process, a voter can ask a poll worker for an second ``audit''
ballot. This ballot is initially just like any other ballot: however, \emph{all} candidate codes are
revealed, and the ballot is marked as an audit ballot. An audit ballot is scanned, but the voter is
allowed to keep the ballot for later verification. This verification process is described and
discussed in our analysis.

@@

When a ballot has been received, the following takes place:
\begin{enumerate}
	\item
		The candidate code is revealed in Table Q. (If this is an audit ballot -- see below -- then all
		are revealed, and we'll perform the following steps for each code.)
	\item
		A ``check'' is placed on the row in Table R that maps the revealed Q value to some value in S.
	\item
		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R,
		to be counted as a vote for that row's candidate.
\end{enumerate}

@@

Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous -- even to the officials performing the encryption -- by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.

@@

When a voter goes to cast a vote, her candidate selection is encrypted locally (i.e., on her
computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
presented with a SHA-1 hash of her encrypted ballot. At this point, the voter may choose either
to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
complete. But when a voter chooses to ``audit,'' she is presented with \emph{all} of the data
used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
which allows randomness to be specified -- perform the encryption and SHA-1 hash herself
to verify that the hash that \emph{would} have been cast actually does represent the ballot she
intended to cast.

@@

Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
``mixnet.''

@@

The ``mixnet'' accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
same key, but with different random inputs). A random permutation -- referred to as $\pi_{N}$ (where
$N$ is the total number of votes) -- is first used to perform the shuffle. Each ciphertext
$c_{i}$ is then ``re-encrypted'' to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
the random input at encrypt time been different} by a particular amount $s_{i}$. See Figure
~\ref{fig:mixnet} for a visual depiction of this process.

The ``shuffling'' is important because it prevents an attacker from linking a decrypted ballot with
a particular encrypted ballot -- and thus a voter. Re-encryption means that an auditor examining a
proof of proper decryption cannot determine how a particular voter cast her ballot by hashing
all ciphertexts in the proof and matching those hashes to the publicly-posted encrypted vote hashes.

In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
times, actually using only the final shuffle in tallying the results. The other shuffles are
referred to as ``shadow mixes'' and are made public. Those mixes are hashed to obtain a bit string
that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
other bit value indicating that it must provide a mapping from one shadow mix to another. This is
known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
obtain the set of challenges allows this process to be completed entirely within the Helios system
-- without human involvement -- for publication and auditor verification.

@@

Each of these systems provides ballot secrecy by performing a three-step process:
\begin{enumerate}
	\item
		Encrypt ballot prior to its being cast.
	\item
		``Mix'' the ballots in some way.
	\item
		Reveal decrypted ballots for tallying.
\end{enumerate}

@@

In Scantegrity, ``public'' version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, ``keyless'' encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.)

In Helios, the ``public'' ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
which -- unlike Scantegrity's core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, Helios uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about Helios's
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees. Scantegrity essentially has an immensely large
key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
decrypted. Helios, however, uses known algorithms with shorter keys that could potentially be
attacked. Compromise of keys in either system would destroy their privacy guarantees.

@@

Essentially, each of these system uses some mechanism to ``shuffle'' votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

In Scantegrity, the ballot ``mix'' is predetermined, as it is defined by the generation of Table R.
When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
ballots, the information revealed that is ultimately revealed allows half of the ballots to be
traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
Should Table P be compromised, one could complete all mappings and violate secrecy entirely -- or
simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
\emph{either} size of Table R to votes in Table Q \emph{or} tallies in Table S be deterministic,
privacy would be compromised for half of all voters.

Where Table R lies between encryptions and decryptions in Scantegrity, \pv\ and Helios make use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in Scantegrity, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally.

@@

At the time a ballot is cast, these systems attempt to ensure a voter that her
vote is recorded exactly as intended.

@@

\pv\ provides each voter with multiple ballots, one of which she actually casts, and the others
she can audit to verify that the candidate permutation on the left-hand side corresponds to the one
encoded in the onion on the right-hand side. Audited ballots cannot be cast, but since she chooses
her actual ballot at random, if her audited ballots verify, she gains some confidence that
her real ballot would as well. Auditing authorities also verify randomly selected ballots before,
during, and after polling to garner further assurance.

Like \pv, Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

@@

A common theme in verifiable voting systems seems to be the presence of a published ``bulletin
board'' of votes. (Note that because these boards contain only encrypted information, they do not
violate ballot secrecy.)

@@

Secondly, recall that for each row in Table R that does not represent an audit ballot, only half of
the Q-to-S mapping is revealed; \emph{which} half is uncovered is chosen randomly. This prevents an
auditor from mapping any cast ballot to its chosen candidate, but it permits \emph{partial}
verification by allowing an observer to note that the following are true:
\begin{itemize}
	\item
		If a row in Table R is \textbf{checked} and its mapping to Table Q is revealed, then the
		corresponding cell in Table Q has a \textbf{revealed} confirmation code (indicating that the
		code was revealed on a ballot).
	\item
		If a row in Table R is \textbf{unchecked} and its mapping to Table Q is revealed, then the
		corresponding cell in Table Q has a \textbf{hidden} confirmation code (indicating that the code
		was \emph{not} revealed on a ballot).
	\item
		If a row in Table R is \textbf{checked} and its mapping to Table S is revealed, then the
		corresponding cell in Table S is \textbf{checked} (indicating an addition to a candidate's
		tally).
	\item
		If a row in Table R is \textbf{unchecked} and its mapping to Table S is revealed, then the
		corresponding cell in Table S is \textbf{unchecked} (indicating \emph{no} addition to a
		candidate's tally).
\end{itemize}
This technique -- verifying a random partial sample of the data -- is called \term{random partial
checking}. If these checks past, it is accepted that all other ballots must also be counted properly.

@@

Scantegrity prevents coercion via the manner it uses to ``encrypt'' ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
way to prove to a third party that the claim is true.

An important point regarding Scantegrity is that it also relies on a \emph{physical property} -- the
invisible ink used when printing confirmation code ``bubbles'' -- to combat vote coercion (i.e., no
one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
the person for having voted a certain way). This is akin to keeping Table P a secret: the ballots
together \emph{are} Table P, and using special ink allows the codes to be printed without making it
easy for a ballot handler to simple read Table P from the ballots prior to the election.

Helios, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
physical security aside: as with Scantegrity, Helios does not reveal to a voter all the
information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus ``proving'' something
untrue to the coercing party. (This is one reason that it is important for the system to use a
collision-resistant hash function.)

@@

The public nature of this information can combat ``ballot stuffing.'' If names are associated with
the posted ballots, then it should be obvious to one or more careful observers (given sufficient
resources) that nonexistent persons are being posted. Furthermore, publication of ballots
per-precinct can reveal ``stuffing'' should the number of ballots being reported by a particular
precinct/polling location be significantly higher than expected \cite{helios}.

@@

One might wish to prevent a party from determining who did or did not cast \emph{any} ballot.
As we've seen, \term{verifiable counting} typically relies on the ``public'' nature of this data.
Additionally, should this data be hidden, it could potentially be more difficult to notice ``ballot
stuffing.''

@@

In each of these key systems, there exists some way to tie a vote back to a voter or to a physical
receipt: there is always some secret. Ideally, there would be a system wherein a vote could be
tallied properly without \emph{anyone} being able to reveal the candidate selected on the ballot.
Admittedly, to achieve this would be difficult: in the case of a single vote, ``tallying'' just it
would reveal the candidate for which it was cast. But if a secret \emph{must} be kept, it is
worthwhile to take precautions to minimize risk of compromise.
